About

### 2025-07-14 about.qmd
Replace chunk by shortcode
Reformat code and fix typos
Shorten chapter on copyright/ transfer to Appendix

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

@@

This tutorial was created by Florian Kohrt.
It is based on previous work by Josephine Zerna and Christoph Scheffel.
Comments on earlier versions were kindly provided by
Malika Ihle, Florian Pargent, Jonas Hagenberg, Felix Schönbrodt,
and Sarah von Grebmer zu Wolfsthurn.

@@

```{r}
#| output: "asis"
#| echo: false

cat(paste0("Quarto ", as.character(quarto::quarto_version()), " was utilized to render the files."))
```

>>>>

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    orcid: "0000-0001-5963-9229"
  - name: "Felix Schönbrodt"
    orcid: "0000-0002-8282-3910"
bibliography: grateful-refs.bib
---

@@

This tutorial was created by Florian Kohrt.
It is based on previous work by Josephine Zerna and Christoph Scheffel.
Comments on earlier versions were kindly provided by
Malika Ihle, Florian Pargent, Jonas Hagenberg, Felix Schönbrodt,
and Sarah von Grebmer zu Wolfsthurn.
Felix Schönbrodt created this short version of the [longer original tutorial](https://lmu-osc.github.io/code-publishing/).

@@

Quarto {{< var version >}} was utilized to render the files.
